Imputation of Incomplete Multilevel Data with R

### 2023-11-21 docs/manuscript.qmd
test r chunks

@@

@@

>>>>

In [R]{.proglang}, multilevel models may be fitted using the package [lme4]{.pkg}. For linear mixed-effects models, the function

```r
lmer(formula, data, ...)
```

@@

::: callout
Box 2. The `methods`.
:::

::: callout
Box 2. The predictor matrix.
:::

@@

### Setup

```{R}
#| prompt: true
#| warning: false
#| message: false
library(mice)
library(ggmice)
```

### Popularity data

```{R}
#| prompt: true
data("popmis", package = "mice")
```

```{R}
#| prompt: true
dat <- popmis[, c("school", "popular", "sex")] 
```

```{R}
#| prompt: true
#| label: fig-pattern
#| fig-cap: "Missing data pattern."
plot_pattern(dat)
```

```{R}
#| prompt: true
#| fig-cap: "Pair-wise correlations."
plot_corr(dat)
```

```{R}
#| prompt: true
meth <- make.method(dat)
```

```{R}
#| prompt: true
pred <- quickpred(dat)
plot_pred(pred, method = meth)
```

```{R}
#| prompt: true
imp <- mice(
  data = dat,
  method = meth,
  predictorMatrix = pred,
  printFlag = FALSE
)
```

```{R}
#| prompt: true
plot_trace(imp)
```

### 2023-11-21 docs/manuscript.tex
test r chunks

\begin{tcolorbox}[enhanced jigsaw, colback=white, rightrule=.15mm, left=2mm, breakable, arc=.35mm, opacityback=0, leftrule=.75mm, toprule=.15mm, bottomrule=.15mm]

@@

@@

@@

>>>>

\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, breakable, arc=.35mm, colback=white, left=2mm, toprule=.15mm, rightrule=.15mm, leftrule=.75mm, opacityback=0]

@@

In \proglang{R}, multilevel models may be fitted using the package
\pkg{lme4}. For linear mixed-effects models, the function

\begin{verbatim}
lmer(formula, data, ...)
\end{verbatim}

@@

\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, breakable, arc=.35mm, colback=white, left=2mm, toprule=.15mm, rightrule=.15mm, leftrule=.75mm, opacityback=0]

Box 2. The \texttt{methods}.

\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, breakable, arc=.35mm, colback=white, left=2mm, toprule=.15mm, rightrule=.15mm, leftrule=.75mm, opacityback=0]

Box 2. The predictor matrix.

@@

\hypertarget{setup}{%
\subsection{Setup}\label{setup}}

\begin{verbatim}
R> library(mice)
R> library(ggmice)
\end{verbatim}

\hypertarget{popularity-data}{%
\subsection{Popularity data}\label{popularity-data}}

\begin{verbatim}
R> data("popmis", package = "mice")
\end{verbatim}

\begin{verbatim}
R> dat <- popmis[, c("school", "popular", "sex")] 
\end{verbatim}

\begin{verbatim}
R> plot_pattern(dat)
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics{manuscript_files/figure-pdf/fig-pattern-1.pdf}

\caption{\label{fig-pattern}Missing data pattern.}

\end{figure}

\begin{verbatim}
R> plot_corr(dat)
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics{manuscript_files/figure-pdf/unnamed-chunk-5-1.pdf}

\caption{Pair-wise correlations.}

\end{figure}

\begin{verbatim}
R> meth <- make.method(dat)
\end{verbatim}

\begin{verbatim}
R> pred <- quickpred(dat)
R> plot_pred(pred, method = meth)
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics{manuscript_files/figure-pdf/unnamed-chunk-7-1.pdf}

\end{figure}

\begin{verbatim}
R> imp <- mice(
+  data = dat,
+  method = meth,
+  predictorMatrix = pred,
+  printFlag = FALSE
+)
\end{verbatim}

\begin{verbatim}
R> plot_trace(imp)
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics{manuscript_files/figure-pdf/unnamed-chunk-9-1.pdf}

\end{figure}
